---
title: "Berries_Slides"
author: "Haoyu Wang"
date: "10/18/2020"
output:
  powerpoint_presentation: default
  slidy_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
library(knitr)
library(tidyverse)
library(magrittr)
library(kableExtra)
library(png)
library(grid)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

## Introduction

As discussed in class, we're going to wrap up Unit 1 by doing the "berries" dataset. What we need is to combine data cleaning, data organization, and EDA. Also, we need to visualize the data.

These data were collected from the USDA database selector: <a href="https://quickstats.nass.usda.gov">https://quickstats.nass.usda.gov</a>

The data were <a href="https://quickstats.nass.usda.gov/results/D416E96E-3D5C-324C-9334-1D38DF88FFF1">stored online</a> and then downloaded as a CSV file.

## Data cleaning and organizing

Main Steps:
- Load and select meaningful data, find the columns that can be eliminated.

- Choose "STRAWBERRIES" for the futher steps.

- Separate columns

- Organize the data

## Outpus for these steps

```{r, echo = FALSE}
img = readPNG("Pic1.png")
grid.raster(img)
```

##    
```{r, echo = FALSE}
img = readPNG("Pic2.png")
grid.raster(img)
```

##

```{r, echo=FALSE}
img = readPNG("Pic3.png")
grid.raster(img)
```

## EDA(Exploratory Data Analysis)

```{r}
img = readPNG("Pic4.png")
grid.raster(img)
```

